Reproducible Research in R: A Tutorial on how to Do the Same Thing More Than Once

### 2021-11-15 manuscript.Rmd
remove footnote closes #265

---
title: "Reproducible Research in R: A Tutorial on how to Do the Same Thing More Than Once"
author:
  - name: Aaron Peikert
    affil: 1, *
    orcid: 0000-0001-7813-818X
  - name: Caspar J. van Lissa
    affil: 2, 3
    orcid: 0000-0002-0808-5024
  - name: Andreas M. Brandmaier
    affil: 1, 4, 5
    orcid: 0000-0001-8765-6982
affiliation:
  - num: 1
    address: |
      Center for Lifespan Psychology---Max Planck Institute for Human Development, Lentzeallee 94, 14195 Berlin, Germany
  - num: 2
    address: |
      Department of Methodology & Statistics---Utrecht University, Faculty of Social and Behavioral Sciences, Utrecht, Netherlands
  - num: 3
    address: |
      Open Science Community Utrecht, Utrecht, Netherlands
  - num: 4
    address: |
      Max Planck UCL Centre for Computational Psychiatry and Ageing Research
      Berlin, Germany, and London, UK
  - num: 5
    address: |
      MSB Medical School Berlin,
      Berlin, Germany
# firstnote to eighthnote
correspondence: |
  peikert@mpib-berlin.mpg.de
journal: psych
type: tutorial
status: submit
bibliography: temp.bib
simplesummary: |
  Reproducibility has long been considered integral to the scientific method.
  An analysis is considered reproducible if an independent person can obtain the same results from the same data.
  Until recently, detailed descriptions of methods and analyses were the primary instrument for ensuring scientific reproducibility.
  Technological advancements now enable scientists to achieve a more comprehensive standard;
  a standard where that allows anyone to access a digital research repository and reproduce all computational steps from raw data to final report including all relevant statistical analyses, with a single command.
  This method has far-reaching implications for scientific archiving,
  reproducibility and replication,
  scientific productivity,
  and the credibility and reliability of scientific knowledge.
  One obstacle to the widespread use of this method is that the underlying tools
  are complex and not part of most researchers' basic training.
  This paper introduces `repro`, an R package that guides researchers through installation and use of the tools required to make a research project reproducible.
  We also suggest the utilization of the proposed workflow for the preregistration of study plans as reproducible computer code (preregistration as code; PAC).
  Since computer code represents the planned analyses exactly as they will be executed, it is more precise than natural language descriptions of those analyses, which then merely complement the PAC as a more readable summary. 
  PAC circumvents the shortcomings of ambiguous preregistrations that may give researchers undesired degrees of freedom in the execution of their analysis.
  Reproducibility facilitated by automation therefore has a wide range of applications to accelerate scientific progress.
abstract: "`r tryCatch(trimws(readr::read_file(here::here('abstract.Rmd'))))`"
keywords: |
  open science; computational reproducibility; preregistration; R; R Markdown; Make; GitHub; Docker
acknowledgement: |
  We would like to thank Maximilian Stefan Ernst for his contributions to the code for the simulation study. 
authorcontributions: |
  Aaron Peikert took the lead in writing and provided the initial draft of the manuscript.
  Andreas Brandmaier and Caspar J. Van Lissa contributed further ideas, critical feedback, and revisions of the original manuscript.

@@

Scientists increasingly strive to make research data, materials, and analysis code openly available.
Sharing these digital research products can increase scientific efficiency by enabling researchers to learn from each other, reuse materials, and increase scientific reliability by facilitating the review and replication of published research results.
To some extent, these potential benefits are contingent on whether these digital research products are reproducible. 
Reproducibility can be defined as the ability of anyone to obtain identical results from the *same* data with the *same* computer code [see @Peikert2019 for details].
The credibility of empirical research results hinges on their objectivity.
Objectivity in this context means, "in principle it [the research finding] can be tested and understood by anybody." [@popperLogicScientificDiscovery2002, p. 22][^popper].
Only a reproducible result can be tested and understood by anyone.
Therefore, reproducibility has long been considered integral to empirical research.
Unfortunately, despite increasing commitment to open science practices and good will, many projects can not yet be reproduced by other research teams [@obels2020].
This is because making a research project reproducible with all code, data, and materials is accompanied by various challenges (e.g., missing software dependencies or ambiguous documentation of the exact computational steps taken), and there is a dire need for reproducibility standards.
With technological advancement, however, it is now possible to make all digital products related to a research project available in a manner that enables automatic reproduction of the research project with minimal effort.

@@

[^popper]: In fact, @popperLogicScientificDiscovery2002's famous criterion of demarcation is built around "inter-subjective testing", a concept that he later generalized to inter-subjective criticism (Footnote *1, p. 22). Somewhat confusingly, @popperLogicScientificDiscovery2002 uses the term "Reproducibility" for what we would call "Replication."

>>>>

---
title: "Reproducible Research in R: A Tutorial on how to Do the Same Thing More Than Once"
author:
  - name: Aaron Peikert
    affil: 1, *
    orcid: 0000-0001-7813-818X
  - name: Caspar J. van Lissa
    affil: 2, 3
    orcid: 0000-0002-0808-5024
  - name: Andreas M. Brandmaier
    affil: 1, 4, 5
    orcid: 0000-0001-8765-6982
affiliation:
  - num: 1
    address: |
      Center for Lifespan Psychology---Max Planck Institute for Human Development, Lentzeallee 94, 14195 Berlin, Germany
  - num: 2
    address: |
      Department of Methodology & Statistics---Utrecht University, Faculty of Social and Behavioral Sciences, Utrecht, Netherlands
  - num: 3
    address: |
      Open Science Community Utrecht, Utrecht, Netherlands
  - num: 4
    address: |
      Max Planck UCL Centre for Computational Psychiatry and Ageing Research
      Berlin, Germany, and London, UK
  - num: 5
    address: |
      MSB Medical School Berlin,
      Berlin, Germany
# firstnote to eighthnote
correspondence: |
  peikert@mpib-berlin.mpg.de
journal: psych
type: tutorial
status: submit
bibliography: temp.bib
simplesummary: |
  Reproducibility has long been considered integral to the scientific method.
  An analysis is considered reproducible if an independent person can obtain the same results from the same data.
  Until recently, detailed descriptions of methods and analyses were the primary instrument for ensuring scientific reproducibility.
  Technological advancements now enable scientists to achieve a more comprehensive standard;
  a standard where that allows anyone to access a digital research repository and reproduce all computational steps from raw data to final report including all relevant statistical analyses, with a single command.
  This method has far-reaching implications for scientific archiving,
  reproducibility and replication,
  scientific productivity,
  and the credibility and reliability of scientific knowledge.
  One obstacle to the widespread use of this method is that the underlying tools
  are complex and not part of most researchers' basic training.
  This paper introduces `repro`, an R package that guides researchers through installation and use of the tools required to make a research project reproducible.
  We also suggest the utilization of the proposed workflow for the preregistration of study plans as reproducible computer code (preregistration as code; PAC).
  Since computer code represents the planned analyses exactly as they will be executed, it is more precise than natural language descriptions of those analyses, which then merely complement the PAC as a more readable summary. 
  PAC circumvents the shortcomings of ambiguous preregistrations that may give researchers undesired degrees of freedom in the execution of their analysis.
  Reproducibility facilitated by automation therefore has a wide range of applications to accelerate scientific progress.
abstract: "`r tryCatch(trimws(readr::read_file(here::here('abstract.Rmd'))))`"
keywords: |
  open science; computational reproducibility; preregistration; R; R Markdown; Make; GitHub; Docker
acknowledgement: |
  We would like to thank Maximilian Stefan Ernst for his contributions to the code for the simulation study. We are grateful to Julia Delius for her helpful assistance in language and style editing.
authorcontributions: |
  Aaron Peikert took the lead in writing and provided the initial draft of the manuscript.
  Andreas Brandmaier and Caspar J. Van Lissa contributed further ideas, critical feedback, and revisions of the original manuscript.

@@

Scientists increasingly strive to make research data, materials, and analysis code openly available.
Sharing these digital research products can increase scientific efficiency by enabling researchers to learn from each other, reuse materials, and increase scientific reliability by facilitating the review and replication of published research results.
To some extent, these potential benefits are contingent on whether these digital research products are reproducible. 
Reproducibility can be defined as the ability of anyone to obtain identical results from the *same* data with the *same* computer code [see @Peikert2019 for details].
The credibility of empirical research results hinges on their objectivity.
Objectivity in this context means, "in principle it [the research finding] can be tested and understood by anybody." [@popperLogicScientificDiscovery2002, p. 22].
Only a reproducible result can be tested and understood by anyone.
Therefore, reproducibility has long been considered integral to empirical research.
Unfortunately, despite increasing commitment to open science practices and good will, many projects can not yet be reproduced by other research teams [@obels2020].
This is because making a research project reproducible with all code, data, and materials is accompanied by various challenges (e.g., missing software dependencies or ambiguous documentation of the exact computational steps taken), and there is a dire need for reproducibility standards.
With technological advancement, however, it is now possible to make all digital products related to a research project available in a manner that enables automatic reproduction of the research project with minimal effort.

@@
